\documentclass{vhdl-assignment}

\title{Final Projects}
\date{2024}

\begin{document}
\maketitle
\thispagestyle{fancy}

\begin{project}{Design a RISC Stored-Program Machine}
    \subsection*{1. Description}
    Reduced instruction-set computers (RISC) are designed to have a small set of instructions that execute in short clock cycles, with a small number of cycles per instruction.
    RISC machines are optimized to achieve efficient pipelining of their instruction streams.
    The machine also serves as a starting point for developing architectural variants and a more robust instruction set.
    Designers make high-level tradeoffs in selecting an architecture that serves an application.
    Once an architecture has been selected, a circuit that has sufficient performance (speed) must be synthesized.
    Hardware description languages (HDLs) play a key role in this process by modeling the system and serving as a descriptive medium that can be used by a synthesis tool.
    \subsection*{2. References and Documents}
    \begin{itemize}
        \item Book : Advanced Digital Design with Verilog HDL - Chapter 7. Design and Synthesis of Datapath Controller - Section 7.3 Design and Synthesis of a RISC Stored Program Machine (Page 355)
        \item Source code : in the book 
    \end{itemize}
    \subsection*{3. Requirements}
    \begin{enumerate}
        \item Implement the design according to the instructions in the document.
        \item Build Specification of the design based on the documentations provided.
        \begin{itemize}
            \item System modeling/design by diagram, FSM, ASM, ASMD, FSMD,\dots
            \item Describe the input/output signals of each module.
        \end{itemize}
        \item Verify your design.
        \item Evaluate the results of the device when deployed on FPGA: by simulation, FPGA kit, evaluate resource consumption.
    \end{enumerate}
\end{project}

\end{document}